% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)

\begin{document}

\name{Maxim Noah Khailo}
% \address used twice to have two lines of address
\address{{\bf www.mempko.com}}
\address{{\bf max@mempko.com}}

\begin{resume}
 
\section{OBJECTIVE}       
                Grow software for a better world.
 
\section{EXPERIENCE} 
                {\bf Co-Founder} \hfill 2019-Present \\
                Merit Capital, 
                Seattle, WA
                 \begin{itemize}  \itemsep -1pt % reduce space between items
                    \item World Building.
                 \end{itemize}
                {\bf CTO} \hfill 2017-2019 \\
                Meritlabs, 
                Seattle, WA
                 \begin{itemize}  \itemsep -1pt % reduce space between items
                    \item Built a next generation digital currency designed
                        with safety, community, and scalability in mind.
                    \item At it's peak it had tens of thousands of users and thousands of miners.
                 \end{itemize}
                {\bf Principal Engineer} \hfill 2015-2017 \\
                FoxCommerce, 
                Seattle, WA
                 \begin{itemize}  \itemsep -1pt % reduce space between items
                    \item Built the core technologies and products for an e-commerce system 
                        using the event sourcing model with a machine learning pipeline.
                    \item Guided the organization's technical decisions.
                    \item Wrote a fast time series database called Henhouse.
                 \end{itemize}
                {\bf Senior Architect} \hfill 2008-2015 \\
                HERE Maps, 
                R\&D Department, Chicago, IL
                 \begin{itemize}  \itemsep -1pt % reduce space between items
                         \item Created a computer vision (CV)
                        system to automate map creation.
                    \item The CV system saved the company large 
                        sums by leveraging map builder productivity.
                    \item The CV system processed tens of petabytes of imagery and 3D LiDAR data.
                    \item Built innovative debugging \& instrumentation tools 
                        for developing computer vision algorithms.
                \end{itemize}
                {\bf Software Engineer} \hfill  2006-2008 \\
                SSS-Software, Lisle IL
                 \begin{itemize}  \itemsep -1pt 
                    \item Designed and implemented a WMS compatible Map Server.
                    \item The Map Server became a core product for the company.
                    \item Wrote decoders for government and proprietary image formats from spec.  
                 \end{itemize} 
                {\bf Research Programmer} \hfill 2002-2006 \\
                North Central College, Naperville, IL
                \begin{itemize} \itemsep -1pt 
                    \item Designed and implemented stock trading simulation software
                        which ran on the university's computer cluster. 
                \end{itemize} 
\section{FREE SOFTWARE} Download at {\bf www.mempko.com} \\ 
                \begin{itemize} \itemsep -1pt 
                    \item {\bf Firestr} A peer-to-peer computation and communication platform.
                    \item {\bf Henhouse} A fast time series database.
                    \item {\bf NCC} A flexible component based 3D game engine.
                    \item {\bf Neural} Neural Net library and demos.
                \end{itemize}

\section{EDUCATION} {\bf Bachelor of Science,} Computer Science \\
                North Central College, Naperville, IL 
                January 2006
\end{resume}
\end{document}

